Best practices for forecasting changes in biodiversity: an example using breeding birds

### 2017-09-03 manuscript/draft.Rmd
mention baselines earlier

The most commonly used methods for forecasting future biodiversity, SDMs and
macroecological models, both produced worse forecasts than time-series models
and simple baselines. This weakness suggests that predictions about future
biodiversity change should be viewed with skepticism unless the underlying
models have been validated temporally, via hindcasting. Since site-level
richness is relatively stable, spatial validation is not enough: a model can
have high accuracy across spatial gradients without being able to predict
changes over time. This gap between spatial and temporal accuracy is known to be
important for species-level predictions [@rapacciuolo2012; @oedekoven2017]; our
results indicate that it is substantial for higher-level patterns like richness
as well. SDMs' poor temporal predictions are particularly sobering, as these
models have been one of the main foundations for estimates of the predicted loss
of biodiversity to climate change over the past decade or so [@thomas2004;
@thuiller2011; @urban2015]. Our results also highlight the importance of
comparing multiple modeling approaches when conducting ecological forecasts, and
in particular, the value of comparing results to simple baselines to avoid
over-interpreting the information present in these forecasts [Box 1].
Disciplines that have more mature forecasting cultures often do this by
reporting "forecast skill", i.e., the improvement in the forecast relative to a
simple baseline [@jolliffe2003]. We recommend following the example of @ye2015
and adopting this approach in future ecological forecasting research.

>>>>

The most commonly used methods for forecasting future biodiversity, SDMs and
macroecological models, both produced worse forecasts than time-series models
and simple baselines. This weakness suggests that predictions about future
biodiversity change should be viewed with skepticism unless the underlying
models have been validated temporally, via hindcasting and comparison with
simple baselines. Since site-level richness is relatively stable, spatial
validation is not enough: a model can have high accuracy across spatial
gradients without being able to predict changes over time. This gap between
spatial and temporal accuracy is known to be important for species-level
predictions [@rapacciuolo2012; @oedekoven2017]; our results indicate that it is
substantial for higher-level patterns like richness as well. SDMs' poor temporal
predictions are particularly sobering, as these models have been one of the main
foundations for estimates of the predicted loss of biodiversity to climate
change over the past decade or so [@thomas2004; @thuiller2011; @urban2015]. Our
results also highlight the importance of comparing multiple modeling approaches
when conducting ecological forecasts, and in particular, the value of comparing
results to simple baselines to avoid over-interpreting the information present
in these forecasts [Box 1]. Disciplines that have more mature forecasting
cultures often do this by reporting "forecast skill", i.e., the improvement in
the forecast relative to a simple baseline [@jolliffe2003]. We recommend
following the example of @ye2015 and adopting this approach in future ecological
forecasting research.
